Confound and control in language experiments

### 2016-08-02 poster-snl2016.tex
small technicality on percentage

%For example, if word length is not significantly different for two conditions, they are considered as matched for word length.
Such a test has high error rates and is conceptually misguided yet is commonly used (67\% of papers in a survey of recent Brain and Language issues).
\end{block}

>>>>

%For example, if word length is not significantly different for two conditions, they are considered as matched for word length.
Such a test has high error rates and is conceptually misguided yet is commonly used (67\% of papers attempting to address confounding in a survey of recent Brain and Language issues).
\end{block}
